Adaptive Disk Storage for Interaction Graphs

### 2014-04-16 notes/graph-adapt/main.tex
fix for eq 2
A first attempt at formulizing the query I/O

\usepackage{alltt}

@@

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}(B)) = |\mathcal{P}(B)|\cdot\left(1-\frac{\sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

@@

>>>>

\usepackage{alltt}
\usepackage{enumerate}

@@

The storage overhead can be formalized as:
\begin{equation}
H(\mathcal{P}(B)) = |\mathcal{P}(B)|\cdot\left(1-\frac{c(B)\cdot \sum_{a\in A} s(a)}{s(B)}\right) 
\end{equation}

@@

\subsection{Query I/0}

\noindent 
We have a set of queries:

$$
Q = \left\{ q_0, \dots,  q_n \right\}
$$

\noindent 
And that the queries access set of attributes:
$$
Q.A = \left\{ q_0.A, \dots,  q_n.A \right\}
$$

\noindent 
Assume that we are given a function $f$ that maps a query to the frequency the
query is executed:
$$
f(q_i)
$$

To work through a concrete example, say we are given a schema \texttt{abcd}
which we partition in two ways:
\begin{enumerate}[(i)]
\item \texttt{ab}, \texttt{ac}, and \texttt{d} 
\item \texttt{abd} and \texttt{ac} 
\end{enumerate}

\noindent 
and say we are given the following query attribute sets and frequencies:
$$
Q.A = \left\{ abd, ac, d \right\}\\
$$
$$
\left\{ f(q_o) \mapsto 0.4,  f(q_1) \mapsto 0.5,  f(q_2) \mapsto 0.1 \right\}
$$
Then the I/O cost for (i) should be:
$$
L(\mathcal{P}(B))  = 0.4 \cdot (s(ab) + s(d)) + 0.5 \cdot s(ac) + 0.1 \cdot s(d) 
$$
Then the I/O cost for (ii) should be:
$$
L(\mathcal{P}(B))  = 0.4 \cdot s(abd) + 0.5 \cdot s(ac) + 0.1 \cdot s(abd) 
$$
\noindent 
Generalizing, I think we want an equation like the following:
$$
L(\mathcal{P}(B)) = \sum_{q\in Q} \left( f(q) \cdot \sum_{a\in A} s(a) \right)
$$
\noindent 
But, I don't think this is quite right. I have the following questions below:\\
\textbf{Questions}:
\begin{enumerate}
\item The term in the second summation is supposed to be the sizes of all the
sub-blocks accessed. I am not quite sure how to write this in our notation. 
\item It might be the case that there are several possible sub-block that we
  could access to satisfy a query. I think somewhere in the formulation, we need
  to say that we access the \texttt{min} subblock that will give us the
  attributes we want.
\end{enumerate}
